Simulations, CLT and EVT

### 2020-08-27 mean_null.Rmd
tidy data structure

```{r functions}
# create data for each levels

@@

```{r tidy_data}

# input vector of levels for which distributions are plotted
nlevels <- seq(2, 10, 1)

plot_simdata <- function(nlevels = seq(2, 10, 1),
                         nsim = 500,
                         sim_dist = distributional::dist_gamma(
                           shape = shape1,
                           rate = rate1
                         ),
                         # distr = "norm",
                         create_fun = mean) {
  data_orig <- nlevels %>%
    purrr::map_df(function(i) {
      create_datai <- create_simdata(nx = i, nsim, sim_dist, create_fun)
      tibble::tibble(ind = i, sim_data = create_datai)
    })

  data_orig %>%
    unnest(sim_data) %>%
    ggplot(aes(x = sim_data)) +
    geom_histogram() +
    facet_wrap(~ind)
  # + ggtitle(paste0(distr, " (",par1,", ",par2,")"))
}
```

@@

```{r}
set.seed(12345)
plot_simdata(
  nlevels = seq(2, 10, 1),
  nsim = 500,
  create_fun = mean
)
```

@@

@@

```{r}
set.seed(54321)
plot_simdata(
  nlevels = seq(20, 45, 5),
  nsim = 500,
  create_fun = mean
)
```

@@

```{r normmean_small_lev}
set.seed(12345)
plot_simdata(
  nlevels = seq(2, 10, 1),
  nsim = 500,
  create_fun = norm_mean
)
```

@@

```{r normmean_large_lev}
set.seed(54321)
plot_simdata(
  nlevels = seq(20, 45, 5),
  nsim = 500,
  create_fun = norm_mean
)
```

@@

```{r max_small_lev}
set.seed(12345)
plot_simdata(
  nlevels = seq(2, 10, 1),
  nsim = 500,
  create_fun = max
)
# sim_dist = distributional::dist_normal(5, 10))
# distr = "gumbel")
```

@@

```{r max_large_lev}
set.seed(54321)
plot_simdata(
  nlevels = seq(20, 45, 5),
  nsim = 500,
  create_fun = max
)
# distr = "gumbel",
# sim_dist = distributional::dist_normal(5, 10))
```

@@

```{r normmax_small_lev}
set.seed(12345)
plot_simdata(
  nlevels = seq(2, 10, 1),
  nsim = 500,
  # distr = "gumbel",
  # sim_dist = distributional::dist_normal(5, 10),
  create_fun = norm_max
)
```

@@

```{r normmax_large_lev}
set.seed(54321)
plot_simdata(
  nlevels = seq(20, 45, 5),
  nsim = 500,
  create_fun = norm_max
  # distr = "gumbel",
  # sim_dist = distributional::dist_normal(5, 10))
)
```

>>>>

```{r create_simdata}
# create data for each levels

@@

```{r create_nlevels}
create_nlevels <- function(nlevels = seq(2, 10, 2),
                           nsim = 500,
                           sim_dist = distributional::dist_gamma(
                             shape = shape1,
                             rate = rate1
                           ),
                           # distr = "norm",
                           create_fun = mean) {
  data_orig <- nlevels %>%
    purrr::map_df(function(i) {
      create_datai <- create_simdata(nx = i, nsim, sim_dist, create_fun)
      tibble::tibble(ind = i, sim_data = create_datai)
    })
  data_orig %>% unnest(sim_data)
}
```

```{r create_scenarios}
set.seed(12345)
data_all_mean <- create_nlevels(nlevels = seq(2, 50, 1), create_fun = mean)

set.seed(12345)
data_all_max <- create_nlevels(nlevels = seq(2, 50, 1),
                               create_fun = max)

set.seed(12345)
data_all_norm_mean <- create_nlevels(nlevels = seq(2, 50, 1),
                               create_fun = norm_mean)

set.seed(12345)
data_all_norm_max <- create_nlevels(nlevels = seq(2, 50, 1),
                               create_fun = norm_max)
```

```{r mean_small}
data_all_mean %>%
  filter(ind %in% seq(2, 10, 1)) %>%
  ggplot(aes(x = sim_data)) +
  geom_histogram() +
  facet_wrap(~ind)
```

@@

@@

```{r mean_large}
data_all_mean %>%
  filter(ind %in% seq(20, 45, 5)) %>%
  ggplot(aes(x = sim_data)) +
  geom_histogram() +
  facet_wrap(~ind)
```

@@

@@

```{r norm_mean_small}
data_all_norm_mean %>%
  filter(ind %in% seq(2, 10, 1)) %>%
  ggplot(aes(x = sim_data)) +
  geom_histogram() +
  facet_wrap(~ind)
```

@@

```{r norm_mean_large}
data_all_norm_mean %>%
  filter(ind %in% seq(20, 45, 5)) %>%
  ggplot(aes(x = sim_data)) +
  geom_histogram() +
  facet_wrap(~ind)
```

@@

```{r max_small}
data_all_max %>%
  filter(ind %in% seq(2, 10, 1)) %>%
  ggplot(aes(x = sim_data)) +
  geom_histogram() +
  facet_wrap(~ind)
```

@@

```{r max_large}
data_all_max %>%
  filter(ind %in% seq(20, 45, 5)) %>%
  ggplot(aes(x = sim_data)) +
  geom_histogram() +
  facet_wrap(~ind)
```

@@

```{r norm_max_small}
data_all_norm_max %>%
  filter(ind %in% seq(2, 10, 1)) %>%
  ggplot(aes(x = sim_data)) +
  geom_histogram() +
  facet_wrap(~ind)
```

@@

```{r norm_max_large}
data_all_norm_max %>%
  filter(ind %in% seq(20, 45, 5)) %>%
  ggplot(aes(x = sim_data)) +
  geom_histogram() +
  facet_wrap(~ind)
```
